### 2021-05-06 doc/thesis/chapters/dsp.tex
update

\begin{figure}[!h]
  \centering
    \includegraphics[width=9cm]{img/fm-channel-baseband.png}
  \caption{Allocation of frequencies in an FM channel \cite{ref_fig_channel_freqs}}
  \label{fig_channel_baseband_freqs}
\end{figure}

@@

\includepicture [0.6] [0] {Frequency discriminator block diagram \cite{ref_fig_freq_discriminator}} {bd_freq_discriminator} {img/discrimination_method_bd1.jpg}

@@

\includepicture [0.75] [0] {Time-domain signals in envelope detection \cite{ref_roppel}} {time_domain_envelope_detect} {img/envelope-detect-time-domain.jpg}

@@

\begin{figure}[!h]
  \centering
    \includegraphics[width=8.8cm]{img/fm-demod-stereo-audio.png}
  \caption{Block diagram of FM stereo audio demodulation \cite{ref_roppel}}
  \label{fig_bd_stereo_demod}
\end{figure}

>>>>

\begin{figure}[!h]
  \centering
    \includegraphics[width=9cm]{img/fm-channel-baseband.png}
  \caption{Allocation of frequencies in an FM channel \cite{ref_fig_channel_freqs}.}
  \label{fig_channel_baseband_freqs}
\end{figure}

@@

\includepicture [0.6] [0] {Frequency discriminator block diagram \cite{ref_fig_freq_discriminator}.} {bd_freq_discriminator} {img/discrimination_method_bd1.jpg}

@@

\includepicture [0.75] [0] {Time-domain signals in envelope detection \cite{ref_roppel}.} {time_domain_envelope_detect} {img/envelope-detect-time-domain.jpg}

@@

\begin{figure}[!h]
  \centering
    \includegraphics[width=8.8cm]{img/fm-demod-stereo-audio.png}
  \caption{Block diagram of FM stereo audio demodulation \cite{ref_roppel}.}
  \label{fig_bd_stereo_demod}
\end{figure}
